---
title: "WilliamEtAl_Dec2025_GRSPfood"
author: "Emily Williams, Theo Michaels, Alice Boyle"
date: "04 December 2025"
output: html_document
toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Datasets are used for this analysis:

- "EdibleMassData2014_raw.csv"
- "GRSP_Food_Manuscript_Final_Dec2025.csv"
- "GRSP_DispersalData_withBFE_April2025.csv"


```{r load libraries, include = FALSE}

# Evaluating models, transformations if needed
library(effects)        # For extracting model predictions and confidence intervals for plotting
library(AICcmodavg)     # For evaluating AIC scores for models
library(ggResidpanel)   # Used for evaluating model assumptions
library(lattice)

# Analysis 
library(car)            # Used with other packages, also Anova()
library(lme4)           # Used for linear and mixed effects models
library(lmerTest)       # Used for anova(), different than Anova()
library(performance)    # Used to obtain r-squared, conditional r-squared, etc. 
library(marginaleffects)# Obtain partial effects

# Specific to graphing
library(ggplot2)
library(gridExtra)
library(sjPlot)
library(interactions)
library(cowplot)
library(svglite)
library(patchwork)

# Other needed packages  
library(anytime)         # For making date objects, but see lubridate package below
library(naniar)          # For replacing values with NA
library(lubridate)       # For assigning dates to numerical values, etc. 
library(tidyr)
library(dplyr)

```


# PREDICTION I ANALYSIS
Prediction I: Food abundance would vary temporally over single breeding seasons, and spatially in response to the individual and interactive disturbances of burning and grazing. 

```{r Prediction I analysis, include = TRUE}
##########################################################
######################### STEP 1 #########################
##########################################################

# BRING IN DATA  ------------------------
df_Food_og <- read.csv("EdibleMassData2014_raw.csv")

# ASSIGN VARIABLES STRUCTURE AS NEEDED ------------------------
df_Food_og$YrsSinceBurn <- as.factor(df_Food_og$YrsSinceBurn)
df_Food_og$GrazingTreatment <- as.factor(df_Food_og$GrazingTreatment)
df_Food_og$Watershed <- as.factor(df_Food_og$Watershed)
df_Food_og$TimePeriod <- as.factor(df_Food_og$TimePeriod)

# Fix zLate to Late
levels(df_Food_og$TimePeriod)[levels(df_Food_og$TimePeriod) == "zLate"]<-"Late"

# SUMMARIZE TRANSECTS SECTIONS ------------------------

df_Food<-df_Food_og %>%
  group_by(Watershed, TransectID, TimePeriod, BurnTreatment, GrazingTreatment, YrsSinceBurn) %>%
   summarize(EdibleMass = sum(EdibleMass)) %>%
  as.data.frame()

# TRANSFORMATIONS ------------------------

df_Food$EdibleMass_trans<-(log(df_Food$EdibleMass))


##########################################################
######################### STEP 2 #########################
##########################################################

# SUMMARY OF EDIABLE BIOMASS BY TIME PERIOD ------------------------
df_EBbyTP_SummaryStats<- df_Food %>%
group_by(TimePeriod) %>%
    summarise(
    EB_mean = mean(EdibleMass, na.rm = TRUE)
  )

##########################################################
######################### STEP 3 #########################
##########################################################

# MODELS FOR PREDICTION 1 ------------------------

# Mod_01: additive ------------------------
mod_Food_01 <- lmer(EdibleMass_trans ~ TimePeriod + GrazingTreatment + YrsSinceBurn + (1|Watershed) + (1|Watershed:TransectID), data = df_Food, REML=FALSE)
summary(mod_Food_01)

# Mod_02: interactions  ------------------------
mod_Food_02 <- lmer(EdibleMass_trans ~ TimePeriod + GrazingTreatment + YrsSinceBurn + TimePeriod*GrazingTreatment + TimePeriod*YrsSinceBurn + (1|Watershed) + (1|Watershed:TransectID), data = df_Food, REML=FALSE)
summary(mod_Food_02)

### AIC COMPARISON ------------------------
prediction_i_R_models <- list(mod_Food_01, mod_Food_02)
prediction_i_R_names <- c("by_TP_GT_YB", "by_TP_GT_YB_TPGT_TPYB")
aictab(cand.set = prediction_i_R_models, modnames = prediction_i_R_names)

### R square results ------------------------
r2_nakagawa(mod_Food_02)


```


# PREDICTION I FIGURE

```{r Prediction I figure, echo = FALSE}

# GRAPHING ------------------------

# timeperiod*Yearsince burn
plot_time_YearSinceBurn<-cat_plot(mod_Food_02, pred = TimePeriod, modx = YrsSinceBurn, 
                                  pred.point.size = 5, geom = "line", errorbar.width = 0.2, 
                                  x.label = "Time Period",
                                  y.label = "ln Edible Mass (g/150m  )", 
                                  colors = c("#e32636", "#ff8c00", "#f0dc82"), legend.main = "Years Since Burn")



plot_time_YearSinceBurn02<-plot_time_YearSinceBurn +
  ylim(-1, 3.15)+
  theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain", family = "arial"), 
        axis.text.y = element_text(colour = "black", size = 11, face = "plain", family = "arial"),
        legend.text = element_text(colour = "black", size = 11, face = "plain", family = "arial"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain", family = "arial"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain", family = "arial"),
        legend.title = element_text(colour = "black", size = 12, face = "plain", family = "arial")
        )


# timeperiod*Grazing
plot_time_Grazing<-cat_plot(mod_Food_02, pred = TimePeriod, modx = GrazingTreatment, 
                            pred.point.size = 5, geom = "line", errorbar.width = 0.2, 
                            x.label = "Time Period", 
                            y.label = "ln Edible Mass (g/150m  )", 
                            colors = c("#8b4513", "#000000", "#228b22"), legend.main = "Grazing Treatment")

plot_time_Grazing02<-plot_time_Grazing +
  ylim(-1, 3.15)+
  theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain", family = "arial"), 
        axis.text.y = element_text(colour = "black", size = 11, face = "plain", family = "arial"),
        legend.text = element_text(colour = "black", size = 11, face = "plain", family = "arial"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain", family = "arial"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain", family = "arial"),
        legend.title = element_text(colour = "black", size = 12, face = "plain", family = "arial")
        )

plot_time_YearSinceBurn02
plot_time_Grazing02



```


# Bring in data and set up dataframe to use for predictions ii-iv.


```{r Bring in data for prediction ii-iv, include=TRUE}

# BRING IN DATA  ------------------------
df_GRSP_Food <- read.csv("GRSP_Food_Manuscript_Final_Dec2025.csv")

# ADD IN NAs  ------------------------

is.na(df_GRSP_Food) <- df_GRSP_Food == -999
is.na(df_GRSP_Food) <- df_GRSP_Food == -9

# ASSIGN VARIABLES STRUCTURE AS NEEDED ------------------------
df_GRSP_Food$PlotName<-as.factor(df_GRSP_Food$PlotName)
df_GRSP_Food$Recap<-as.factor(df_GRSP_Food$Recap)
df_GRSP_Food$Age<-as.factor(df_GRSP_Food$Age)
df_GRSP_Food$Sex<-as.factor(df_GRSP_Food$Sex)
df_GRSP_Food$BurnTreatment<-as.factor(df_GRSP_Food$BurnTreatment)
df_GRSP_Food$GrazingTreatment<-as.factor(df_GRSP_Food$GrazingTreatment)
df_GRSP_Food$CaptureYear<-as.factor(df_GRSP_Food$CaptureYear)
df_GRSP_Food$yearSinceBurn<-as.factor(df_GRSP_Food$yearSinceBurn)

df_GRSP_Food$FatScoreOrd<-as.factor(df_GRSP_Food$FatScore)
df_GRSP_Food$timeperiod<-factor(df_GRSP_Food$timeperiod, levels = c("Early", "Mid", "Late"))

# SURVEY DATE AS A DATE ------------------------
df_GRSP_Food$CaptureDate <- as.Date(df_GRSP_Food$CaptureDate)

# CAPTURE TIME  ------------------------
df_GRSP_Food$CaptureTimeCST <- as.POSIXct(df_GRSP_Food$CaptureTime, tz = "America/Chicago", format = "%H:%M")
#str(df_GRSP_Food)


# PLOT TYPE ------------------------
# Some plots are not relevant for predictions ii-iV need to be removed.

df_GRSP_Food<-subset(df_GRSP_Food, df_GRSP_Food$PlotName !="4A" & df_GRSP_Food$PlotName !="N20A" & 
                       df_GRSP_Food$PlotName !="BFE" & df_GRSP_Food$PlotName !="NT")


```


# PREDICTION II ANALYSIS
Prediction II: Fueling rates, would be positively associated with the spatial and temporal abundance of prey on the landscape.

```{r Prediction II analysis, include=TRUE}
##########################################################
######################### STEP 1 #########################
##########################################################

# SUBSET DATA AS NEEDED  ------------------------
# Subset data for 2014, TRIG = FALSE, adults only
df_GRSP_Food_2014<-df_GRSP_Food[df_GRSP_Food$CaptureYear=="2014",]
df_GRSP_Food_2014<-df_GRSP_Food_2014[df_GRSP_Food_2014$TRIG.issues == "FALSE",]
df_GRSP_Food_2014<-df_GRSP_Food_2014[df_GRSP_Food_2014$Age !="HY",]

# CLEAN DATASET AND TRANSFORMATIONS ------------------------

# Dropping outliers and passing back to the dataframe
df_GRSP_Food_2014_02<-df_GRSP_Food_2014[-c(143,39),]

# Incorporate transformation 
df_GRSP_Food_2014_02$ConcTRIG_trans<-(log(df_GRSP_Food_2014_02$ConcTRIG))
df_GRSP_Food_2014_02$MeanEdibleMass_trans<-(log(df_GRSP_Food_2014_02$MeanEdibleMass))

##########################################################
######################### STEP 2  ########################
##########################################################
# Here we are going to look at edible biomass as a predictor of TRIG 

# Mod_01: punitive model  ------------------------
mod_TRIGfood_01 <- lm(ConcTRIG_trans~ CaptureTimeCST + CaptureDate + FatScoreOrd + Sex, data = df_GRSP_Food_2014_02)
summary(mod_TRIGfood_01)

# Mod_02: with food ------------------------
mod_TRIGfood_02 <- lm(ConcTRIG_trans~ MeanEdibleMass_trans + CaptureTimeCST + CaptureDate + FatScoreOrd + Sex, 
                      data = df_GRSP_Food_2014_02)
summary(mod_TRIGfood_02)

```


# PREDICTION II FIGURE

```{r Prediction II Figure, echo = FALSE}

# GRAPHING STEP 1: MODEL  ------------------------
# Same as above but redoing to rename, etc.
mod_TRIGfood_NoFood <- lm(ConcTRIG_trans~CaptureTimeCST + CaptureDate + FatScoreOrd + Sex, 
                      data = df_GRSP_Food_2014_02)

df_TRIGfood_GRAPH_residuals<-data.frame(mod_TRIGfood_NoFood$residuals)

# Rename the column and then merge dataframes based on row number
names(df_TRIGfood_GRAPH_residuals)[1] <- "residuals"
df_TRIGfood_GRAPH_residuals_02<-merge(df_GRSP_Food_2014_02, df_TRIGfood_GRAPH_residuals, by = 0)


# GRAPHING STEP 2 ------------------------
# Warning produced is just NA data. 

plot_prediction_ii_Resid_01<-ggplot(df_TRIGfood_GRAPH_residuals_02, aes(x = MeanEdibleMass_trans, y = residuals))+
  geom_point(color = "black") + 
  labs(x = "ln Edible Mass (g/150m  )",
       y = "Residual TRIG")+
  ylim(-1.1, 1)+
  xlim(-0.6, 3.25)+
  theme_classic() +
  theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain"),
        axis.text.y = element_text(colour = "black", size = 11, face = "plain"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain"),
        )

plot_prediction_ii_Resid_01

```


# PREDICTION III ANALYSIS
Prediction III: Territory densities would be positively associated with fueling rates

```{r Prediction III Analysis, include=TRUE}
##########################################################
######################### STEP 1 #########################
##########################################################

# SUBSET DATA AS NEEDED  ------------------------
# Subset data for just males, adults only, TRIG

df_GRSP_Food_Males<-df_GRSP_Food[df_GRSP_Food$Sex=="M",]
df_GRSP_Food_Males<-df_GRSP_Food_Males[df_GRSP_Food_Males$Age !="HY",]
df_GRSP_Food_Males<-df_GRSP_Food_Males[df_GRSP_Food_Males$TRIG.issues == "FALSE",]

##########################################################
######################### STEP 2a ########################
##########################################################
# Determining model for residual TRIG 

# CLEAN DATASET AND TRANSFORM VARIABLES AS NEEDED ------------------------

# Incorporate transformation 
df_GRSP_Food_Males$ConcTRIG_trans<-(log(df_GRSP_Food_Males$ConcTRIG))

# MODELS FOR DETERIMING RESIDUAL TRIG  ------------------------

# Mod_01_resid: with Fat Score ------------------------
mod_TRIGresidMales_01<-lm(ConcTRIG_trans~CaptureTimeCST + CaptureYear + FatScoreOrd, data = df_GRSP_Food_Males)
summary(mod_TRIGresidMales_01)

# Mod_02_resid: without Fat Score ------------------------
mod_TRIGresidMales_02<-lm(ConcTRIG_trans~CaptureTimeCST + CaptureYear, data = df_GRSP_Food_Males)
summary(mod_TRIGresidMales_02)

##########################################################
######################### STEP 2b ########################
##########################################################

### EXTRACT RESIDUALS ------------------------
# Extracting residuals from best fit model: mod_TRIGcovarMales_02
mod_TRIGresidMales_02_Nas<-lm(ConcTRIG_trans~CaptureTimeCST + CaptureYear, data = df_GRSP_Food_Males, na.action = na.exclude)
df_MaleResid02_Nas<-data.frame(resid(mod_TRIGresidMales_02_Nas))

# Rename the column and then merge dataframes based on row number
names(df_MaleResid02_Nas)[1] <- "MaleResid_mod02"
df_GRSP_Food_Males_resid02<-merge(df_GRSP_Food_Males, df_MaleResid02_Nas, by = 0)

# Rename for ease ------------------------
df_GRSP_Food_Males_resids<-df_GRSP_Food_Males_resid02

##########################################################
######################### STEP 3a ########################
##########################################################

# SUMMARIZE  ------------------------
# Summarize so that there is one residual values and time period per density measure. 
df_GRSP_Food_Males_resids_sub<-select(df_GRSP_Food_Males_resids, c(2:10, 17, 20, 25))
df_GRSP_Food_Males_resids_02<-df_GRSP_Food_Males_resids_sub[complete.cases(df_GRSP_Food_Males_resids_sub), ]

df_GRSP_Food_Males_resids_03 <- df_GRSP_Food_Males_resids_02 %>%
  group_by(PlotName, timeperiod) %>%
   summarize(MeanDensity = mean(MeanDensity),
             MeanMaleResid_mod02 = mean(MaleResid_mod02))

# TRANSFORM VARIABLES AS NEEDED  ------------------------

# Incorporate transformation 
df_GRSP_Food_Males_resids_03$MeanDensity_trans<-(sqrt(df_GRSP_Food_Males_resids_03$MeanDensity))

##########################################################
######################### STEP 3b ########################
##########################################################

#### MODELS FOR PREDICTION III  ------------------------

# Model 01: no covariates  ------------------------
mod_TRIG_MalesDensity_01 <- lm(MeanDensity ~ MeanMaleResid_mod02, data = df_GRSP_Food_Males_resids_03)
summary(mod_TRIG_MalesDensity_01) 

# Model 02: with time  ------------------------
mod_TRIG_MalesDensity_02 <- lm(MeanDensity ~ MeanMaleResid_mod02 + timeperiod, data = df_GRSP_Food_Males_resids_03)
summary(mod_TRIG_MalesDensity_02)

# Model 03: with interaction  ------------------------
mod_TRIG_MalesDensity_03 <- lm(MeanDensity ~ MeanMaleResid_mod02 + timeperiod + MeanMaleResid_mod02*timeperiod, 
                               data = df_GRSP_Food_Males_resids_03)
summary(mod_TRIG_MalesDensity_03)

### AIC COMPARISON ------------------------
# Define list of models for AIC comparison, vector with names
# Then calculate AIC for each model
prediction_iii_models <- list(mod_TRIG_MalesDensity_01, mod_TRIG_MalesDensity_02, mod_TRIG_MalesDensity_03)
prediction_iii_names <- c("by_TRIG", "by_TRIG_TP", "by_TRIG_TP_INTERACTION")
aictab(cand.set = prediction_iii_models, modnames = prediction_iii_names)


### ADDITIONAL BEST MODEL FINDINGS ------------------------
# Model 1, summary above
AIC(mod_TRIG_MalesDensity_01)
logLik(mod_TRIG_MalesDensity_01)
df.residual(mod_TRIG_MalesDensity_01) # But also in summary output
deviance(mod_TRIG_MalesDensity_01)

```


# PREDICTION III FIGURE

```{r Prediction III Figure, echo = FALSE}

# GRAPHING ------------------------
# Using mod_TRIG_MalesDensity_01

plot_prediction_iii_01<-ggplot(df_GRSP_Food_Males_resids_03, aes(x = MeanMaleResid_mod02, y = MeanDensity))+
  geom_point(color = "black") + 
  ylim(0,11.5)+
  xlim(-0.50,0.60)+
  labs(x = "Residual TRIG (mmol/l)",
       y = "Density (territorial males/10-ha)")+
 theme_classic() +
 theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain"), 
        axis.text.y = element_text(colour = "black", size = 11, face = "plain"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain"),
        )

plot_prediction_iii_01


```


# PREDICTION IV ANALYSIS
Prediction IV: Territory densities would be positively associated with the abundance of potential prey. 

```{r Prediction IV analysis, include=TRUE}
##########################################################
######################### STEP 1 #########################
##########################################################

# SUBSET DATA AS NEEDED  ------------------------
# Just adult males, using df_GRSP_Food_Males from above.
df_GRSP_Food_Males_2014<-df_GRSP_Food_Males[df_GRSP_Food_Males$CaptureYear=="2014",]

# SUMMARIZE  ------------------------
# Summarize so that there is one ediable biomass values and time period per density measure. 
df_GRSP_Food_Males_2014_02<-select(df_GRSP_Food_Males_2014, c(1:7, 16, 19:20))
df_GRSP_Food_Males_2014_03<-df_GRSP_Food_Males_2014_02[complete.cases(df_GRSP_Food_Males_2014_02), ]

df_GRSP_Food_Males_2014_04 <- df_GRSP_Food_Males_2014_03 %>%
  group_by(PlotName, timeperiod) %>%
   summarize(MeanDensity = mean(MeanDensity),
             MeanEdibleMass = mean(MeanEdibleMass))
       
# TRANSFORMING VARIABLES AS NEEDED ------------------------

# Incorporate transformation. 
df_GRSP_Food_Males_2014_04$MeanEdibleMass_trans<-(log(df_GRSP_Food_Males_2014_04$MeanEdibleMass))


##########################################################
######################### STEP 2 #########################
##########################################################

# Mod_01: no covariates ------------------------
mod_denseFood_01 <- lm(MeanDensity ~ MeanEdibleMass_trans, data = df_GRSP_Food_Males_2014_04)
summary(mod_denseFood_01)

# Mod_02 with time ------------------------
mod_denseFood_02 <- lm(MeanDensity ~ MeanEdibleMass_trans + timeperiod, data = df_GRSP_Food_Males_2014_04)
summary(mod_denseFood_02)

# Mod_03 with interactions ------------------------
mod_denseFood_03 <- lm(MeanDensity ~ MeanEdibleMass_trans + timeperiod + MeanEdibleMass_trans*timeperiod, data = df_GRSP_Food_Males_2014_04)
summary(mod_denseFood_03)

### AIC COMPARISON ------------------------
# Define list of models for AIC comparison, vector with names
# Then calculate AIC for each model
# Best model is mod_denseFood_01 - just ediable biomass. 
prediction_iv_models<- list(mod_denseFood_01, mod_denseFood_02, mod_denseFood_03)
prediction_iv_names<- c("by_EdBio", "by_EdBio_TP", "by_EdBio_TP_EdBioTP")
aictab(cand.set = prediction_iv_models, modnames = prediction_iv_names)

### ADDITIONAL BEST MODEL FINDINGS ------------------------
# Model 1, summary above
AIC(mod_denseFood_01)
logLik(mod_denseFood_01)
df.residual(mod_denseFood_01)
deviance(mod_denseFood_01)

```


# PREDICTION IV FIGURE

```{r Prediction IV Figure, echo = FALSE}

# GRAPHING ------------------------

plot_prediction_iv_01<-ggplot(df_GRSP_Food_Males_2014_04, aes(x = MeanEdibleMass_trans, y = MeanDensity))+
  geom_point(color = "black") + 
  ylim(0,9.75)+
  xlim(-0.5,3.5)+
  labs(x = "ln Edible Mass (g/150m  )",
       y = "Density (territorial males/10-ha)")+
 theme_classic() +
 theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain"), 
        axis.text.y = element_text(colour = "black", size = 11, face = "plain"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain")
        )

plot_prediction_iv_01

```


# PREDICTION V ANALYSIS
Prediction V: Fueling rates would increase from first to second territories to a greater extent in dispersers than in site-faithful individuals.


```{r Prediction V analysis, include=TRUE}
##########################################################
######################### STEP 1 #########################
##########################################################

# BRING IN DATA  ------------------------
df_GRSP_Dispersal <- read.csv("GRSP_DispersalData_withBFE_April2025.csv")

# ASSIGN VARIABLES STRUCTURE AS NEEDED ------------------------
df_GRSP_Dispersal$ColorBand<-as.factor(df_GRSP_Dispersal$ColorBand)
df_GRSP_Dispersal$DispersalStatus<-as.factor(df_GRSP_Dispersal$DispersalStatus)
df_GRSP_Dispersal$Year<-as.factor(df_GRSP_Dispersal$Year)

# TRANSFORMING VARIABLES AS NEEDED ------------------------
# None needed. 


##########################################################
######################### STEP 2 #########################
##########################################################

# T-TestWITH Diff_ResidTRIG ------------------------
# One sided asking if disperses have greater ResidTRIG than the non-disperses
mod_Diff_ResidTRIG_01<-t.test(Diff_ResidTRIG~DispersalStatus, data = df_GRSP_Dispersal, var.equal = TRUE, alternative = "greater")
mod_Diff_ResidTRIG_01

```


# PREDICTION V FIGURE

```{r Prediction V Figure, echo = FALSE}


# GRAPHING ------------------------

plot_prediction_v_01<- ggplot(df_GRSP_Dispersal, aes(x=DispersalStatus, y=Diff_ResidTRIG, fill=DispersalStatus)) +
  geom_hline(yintercept = 0, colour = "darkgray", linetype = "longdash")+  
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=1.2, width = 0.1) +
  ylim(-0.85,1.10)+
  labs(x = "Dispersal Status",
       y = "Residual TRIG (mmol/l)") +
  scale_x_discrete(labels=c("disperser" = "Disperser", "non-disperser" = "Site-Faithful"))+
  scale_fill_manual(values=c("darkslategray4", "darkslategray3")) +
  theme_classic() +
  theme(axis.text.x = element_text(colour = "black", size = 11, face = "plain"), 
        axis.text.y = element_text(colour = "black", size = 11, face = "plain"),
        axis.title.x = element_text(colour = "black", size=12, face = "plain"),
        axis.title.y = element_text(colour = "black", size=12, face = "plain"),
        legend.position = "none"
        )

plot_prediction_v_01

```
